---
title: "Jade: A clean, whitespace-sensitive template language for writing HTML"
author: "Jeroen Ooms"
date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
    toc: yes
vignette: >
  %\VignetteIndexEntry{Introduction to Jade Templating in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(comment = "")
library(rjade)
```

[Jade](http://jade-lang.com/) is a high performance template engine heavily influenced by Haml. The `rjade` package iterfaces to the [JavaScript library](https://www.npmjs.com/package/jade) using V8, the embedded JavaScript engine for R. Below an example of a Jade template, taken from the [jade homepage](http://jade-lang.com/). This example template includes one variable called `youAreUsingJade`.  

```jade
doctype html
html(lang="en")
  head
    title= pageTitle
    script(type='text/javascript').
      if (foo) {
         bar(1 + 5)
      }
  body
    h1 Jade - node template engine
    #container.col
      if youAreUsingJade
        p You are amazing
      else
        p Get on it!
      p.
        Jade is a terse and simple
        templating language with a
        strong focus on performance
        and powerful features.
```

Converting a template to HTML text involves two steps. The first step compiles the template with some formatting options into a closure. The binding for this is implemented in `jade_compile`.

```{r}
# Compile a Jade template in R
text <- readLines(system.file("examples/test.jade", package = "rjade"))
tpl <- jade_compile(text, pretty = TRUE)
```

The second step calls the closure with optionally some local variables to render the output to HTML.

```{r}
# Render the template
tpl()
```

Note how the HTML output changes when setting local variables:

```{r}
tpl(youAreUsingJade = TRUE)
```
